Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
stuff

>>>>

We try using differently sized training sets by varying frequency thresholds for the words.
As training sets often contain some amount of error and noise (the English wordlist
contains an html tag as a word), the frequency threshhold is a good approximation
of error; words with low frequency are may be mispelling or words from other languages.
We find that for datasets ranging from 2500 words to 48,000 words give similar quality results,
with a sharp drop off in scores afterwards.
